%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvpubsection{Invited Presentations}

\cvpub{2023}
      {22}
      { 
        Why do Massive Stars have ``Inflated'' Cores?
      }
      {
        IvS Seminar. KU Leuven. Mar.~31.
      }

\cvpub{}
      {21}
      { 
        Convectively-driven gravity waves in massive stars
      }
      {
        CIERA Theory Group Meeting. Northwestern University. Feb.~17.
      }



\cvpub{2022}
      {20}
      { 
        Why do Massive Stars have ``Inflated'' Cores?
      }
      {
        Astronomy Department colloquium. University of Wisconsin-Madison. Dec.~1.
      }

\cvpub{}
      {19}
      {
        Mixing and wave generation at the convective boundary in massive stars.  
      }
      {
        Applied Mathematics Seminar. Durham University. Nov.~15.
      }

\cvpub{}
      {18}
      {
         Convective boundary mixing and wave generation in the cores of massive stars. 
      }
      {
        Fluids \& MHD Seminar. Leeds University. Nov.~10.
      }

\cvpub{}
      {17}
      {
        Why are convective cores in massive stars bigger than expected?  
      }
      {
        Discussion Seminar. Isaac Newton Institute DYT2 programme. Nov.~7.
      }



\cvpub{}
      {16}
      {
        The mystery of convective boundary mixing in the cores of massive stars.
      }
      {
        TAPIR Seminar. Caltech. Oct.~28.
      }

\cvpub{}
      {15}
      {
        Why are convective cores in stars bigger than expected?  
      }
      {
        Bildsten Group Meeting. KITP. Oct.~27.
      }

\cvpub{}
      {14}
      {
        Chalk Talk: Convective Boundary Mixing in Massive Stars.  
      }
      {
        Compact Objects Research Group Seminar. CCA, Flatiron Institute. Oct.~13.
      }

\cvpub{}
      {13}
      {
        Chalk Talk: Dedalus \& Convective Boundary Mixing in Massive Stars.  
      }
      {
        Quataert Group Meeting. Princeton University. Oct.~12.
      }



\cvpub{}
      {12}
      {  
        Modern mysteries in stellar convection \& a brief intro to fluid dynamics
      }
      {
        CIERA REU Seminar. Northwestern University. July~28.
      }



\cvpub{}
      {11}
      { A modern mystery in stellar convection \& Dedalus is a flexible tool }
      {
        Research Seminar. Newcastle University. July~12.
      }

\cvpub{2021}
	  {10}
	  {Stellar convective penetration: parameterized theory and dynamical simulations}
	  {
	  	Virtual. Astro coffee. The Ohio State University. Oct.~27.
	  }

\cvpub{}
	  {9}
	  {Convective Penetration Probably Parameterizes Convective Overshoot}
	  {
	  	Virtual. Stellar Physics Group Presentation. CCA, Flatiron Institute. July~6.
	  }

\cvpub{}
	  {8}
	  {Convective Penetration Probably Parameterizes Convective Overshoot}
	  {
	  	Virtual. Seminar. ``Kavli Summer Program in Astrophysics 2021: Fluid dynamics of the Sun and stars.'' July~5.
	  }


\cvpub{}
	  {7}
	  {Massive Star Variability}
	  {
	  	Virtual. Pre-recorded research intro lecture. ``Kavli Summer Program in Astrophysics 2021: Fluid dynamics of the Sun and stars.'' June~8.
	  }

\cvpub{2020}
	  {6}
	  {Massive Star Variability and other fun with Dedalus}
	  {
	  	CIERA, Northwestern University. CIERA Virtual Happy Hour Short Talk. Nov.~20.
	  }

\cvpub{}
	  {5}
	  {Entropy Rain and the Solar Convective Conundrum: Dilution and Compression of Individual Convective Downflows}
	  {
	  	Nordita, Stockholm. ``The Shifting Paradigm of Stellar Convection: From Mixing Length Concepts to Realistic Turbulence Modeling" workshop. Mar.~4.
	  }
\cvpub{2019}
	  {4}
	  {Entropy Rain and the Solar Convective Conundrum: Dilution and Compression of Individual Convective Downflows}
	  {
	  	Princeton University. Star Formation/ISM Rendezvous (SFIR) Seminar. Dec.~4.
	  }
\cvpub{}
	  {3}
	  {Entropy Rain: Dilution and Compression of Thermals in Stratified Domains}
	  {
	  	University of Colorado -- Boulder. Applied Math Geophysical and Astrophysical Fluid Dynamics (GAFD) Seminar. Oct.~1.
	  }
\cvpub{2018}
	  {2}
	  {Predicting the Rossby Number in Stratified, Compressible Convection}
	  {
	  	National Solar Observatory. Solar Focus Meeting. Dec.~7.
	  }
\cvpub{2017}
      {1}
      {Fundamental studies in stratified convection at low and high Mach Number}
      {
        University of Colorado -- Boulder. Applied Math Dynamics Seminar. Nov.~11.
      }
