%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\section{Publications List}

\cvpub{2021}
	  {11}
	  {Convective Penetration Probably Parameterizes Convective Overshoot}
	  {
		\textbf{Anders, E.H.}; Jermyn, A.S.; Lecoanet, D.; and Brown, B.P., in prep.~for submission SU 2021.
	  }

\cvpub{}
	  {10}
	  {Marginally-Stable Thermal Equilibria of Rayleigh-B\'{e}nard Convection}
	  {
		O'Connor, L.; Lecoanet, D.; and \textbf{Anders, E.H.}, Submitted to PRFluids.
	  }

\cvpub{}
	  {9}
	  {Surface Manifestation of Stochastically Excited Internal Gravity Waves}
	  {
		Lecoanet, D.; Cantiello, M.; \textbf{Anders, E.H.}; Quataert, E.; Couston, L.; Bouffard, M.; Favier, B.; and Le Bars, M.,
		  \href{https://ui.adsabs.harvard.edu/abs/2021arXiv210504558L/abstract}{Under review at MNRAS.}
	  }

\cvpub{}
	  {8}
	  {A Refined Model of Convectively-Driven Flicker in Kepler Light Curves}
	  {
		 Van Kooten, S.J.; \textbf{Anders, E.H.}; and Cranmer, S.R,
		  \href{https://iopscience.iop.org/article/10.3847/1538-4357/abf7bf}{ApJ 913, 69}
	  }

\cvpub{}
	  {7}
	  {eigentools: A Python package for studying eigenvalueproblems with an emphasis on stability}
	  {
		Oishi, J.S.; Burns, K.J.; Clark, S.E.; \textbf{Anders, E.H.}; Brown, B.P.; Vasil, G.M.; and Lecoanet, D,
		  \href{https://joss.theoj.org/papers/10.21105/joss.03079}{JOSS 6(62), 3079}.
	  }

\cvpub{2020}
	  {6}
	  {Convective dynamics with mixed temperature boundary conditions: why thermal relaxation matters and how to accelerate it}
	  {
		  \textbf{Anders, E.H.}; Vasil, G.M.; Brown, B.P.; and Korre, Lydia, 
		  \href{https://arxiv.org/abs/2003.00026}{Submitted to PRFluids.}
	  }

\cvpub{2019}
	  {5}
	  {Entropy Rain: Dilution and Compression of Thermals in Stratified Domains}
	  {
		  \textbf{Anders, E.H.}; Lecoanet, D.; and Brown, B.P., 
		  \href{https://iopscience.iop.org/article/10.3847/1538-4357/ab3644}{ApJ 884, 65.}
	  }
\cvpub{}
	  {4}
	  {Predicting the Rossby Number in Convective Experiments}
	  {
		  \textbf{Anders, E.H.}; Manduca, C.M.; Brown, B.P.; Oishi, J.S.; Vasil, G.M., 
		  \href{https://iopscience.iop.org/article/10.3847/1538-4357/aaff61}{ApJ 872, 2.}
	  }
\cvpub{2018}
	  {3}
	  {Accelerated evolution of convective simulations}
	  {
		  \textbf{Anders, E.H.}; Brown, B.P; and Oishi, J. S.,
		  \href{https://journals.aps.org/prfluids/abstract/10.1103/PhysRevFluids.3.083502}{Physical Review Fluids 3, 083502.}
	  }
\cvpub{2017}
	  {2}
	  {Convective heat transport in stratified atmospheres at low and high Mach number}
	  {
		  \textbf{Anders, E.H.} and Brown, B.P.,
		  \href{https://journals.aps.org/prfluids/abstract/10.1103/PhysRevFluids.2.083501}{Physical Review Fluids 2, 083501.}
	  }
\cvpub{2016}
	  {1}
	  {The Advanced LIGO photon calibrators}
	  {
			Karki, S.; Tuyenbayev, D.; Kandhasamy, S.; Abbott, B.P.; Abbott, T.D.; \textbf{Anders, E.H.};
			Berliner, J.; Betzwieser, J.; Cahillane, C.; Canete, L.; Conley, C.; Daveloza, H.P.; De Lillo, N.;
			Gleason, J.R.; Goetz, E.; Izumi, K.; Kissel, J.S.; Mendell, G.; Quetschke, V; Rodruck, M.; Sachdev, S.;
			Sadecki, T.; Schwinberg, P.B.; Sottile, A.; Wade, M.; Weinstein, A.J., West, M.; and Savage, R.L.,
			\href{https://aip.scitation.org/doi/10.1063/1.4967303}{Review of Scientific Instruments 87, 114503.}
	  }
