%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
%\newpage
\cvpubsection{Select \& First-Author Publications List}
\hspace{\smallsephintwidth}$\dagger$ - I was a co-first-author on this paper \\
\hspace{\smallsephintwidth}$*$ - I mentored this paper's first author during this project
\vspace{0.3cm}


\cvpubsubsection{Peer-reviewed Journal Articles}
\cvpub{2023}
      {$^*$20}
      {
        Powers, W.T.; \textbf{Anders, E.H.}; and Brown, B.P..
        Submitted to PRFluids.\hspace{-0.5cm}
      }
      {Internally heated and fully compressible convection: flow morphology and scaling laws}

\cvpub{}
      {$^*$19}
      {
        Cresswell, I.G.; \textbf{Anders, E.H.}; Brown, B.P.; Oishi, J.S.; and Vasil, G.M.
        \href{https://journals.aps.org/prfluids/abstract/10.1103/PhysRevFluids.8.093503}{PRF 8, 093503}. 
      }
      {Force Balances in Strong-Field Magnetoconvection Simulations}

\cvpub{}
      {18}
      {
        \textbf{Anders, E.H.}; Lecoanet, D.; Cantiello, M.; Burns, K.J.; Hyatt, B.A.; Kaufman, E.; Townsend, R.H.D.; Brown, B.P.; Vasil, G.M.; Oishi, J.S.; Jermyn, A.S. 
        \href{https://www.nature.com/articles/s41550-023-02040-7}{Nature Astronomy.}
      }
      {The photometric variability of massive stars due to gravity waves excited by core convection}

\cvpub{}
      {$^*$17}
      { Fuentes, J.R.; \textbf{Anders, E.H.}; Cumming, A.; Hindman, B.W. 
        \href{https://iopscience.iop.org/article/10.3847/2041-8213/acd774}{ApJL 950 L4.}
      }
      {Rotation reduces mixing of composition gradients in Jupiter and other gas giants}

\cvpub{}
      {16}
      {
        Fuentes, J.R.; Cumming, A.; Castro-Tapia, M.; \textbf{Anders, E.H.}. 
        \href{https://iopscience.iop.org/article/10.3847/1538-4357/accb56}{ApJ 950 73.}
      }
      {Heat transport and convective velocities in compositionally-driven convection in neutron star and white dwarf interiors}

\cvpub{}
      {$^{\dagger}$15}
      {
        \textbf{Anders, E.H.} and Pedersen, M.G. 
        \href{https://www.mdpi.com/2075-4434/11/2/56}{Invited Review; Galaxies 11(2), 56.}
      }
      {Convective boundary mixing in main-sequence stars: theory and empirical constraints}

\cvpub{2022}
      {$^\dagger$13}
      {
        Fraser, A.E.; Joyce, M.; \textbf{Anders, E.H.}; Tayar, J.; Cantiello, M. 
        \href{https://iopscience.iop.org/article/10.3847/1538-4357/aca024}{ApJ 941 164.}
      }
      {Characterizing Observed Extra Mixing Trends in Red Giants using the Reduced Density Ratio from Thermohaline Models.}

\cvpub{}
      {$^*$12}
      {
        Kaufman, E.; Lecoanet, D.; \textbf{Anders, E.H.}; Brown, B.P.; Vasil, G.M.; Oishi, J.S.; and Burns, K.J.
        \href{https://academic.oup.com/mnras/article/517/3/3332/6748231?login=true}{MNRAS 517, 3.}
      }
      {The Stability of Prendergast Magnetic Fields}

\cvpub{}
	  {11}
	  {
		Jermyn, A.S.; \textbf{Anders, E.H.}; Lecoanet, D.; and Cantiello, M.
        \href{https://iopscience.iop.org/article/10.3847/1538-4365/ac7cee}{ApJS 262, 19.}
       }
	  {An Atlas of Convection in Main Sequence Stars.}

\cvpub{}
	  {10}
	  {
		Jermyn, A.S.; \textbf{Anders, E.H.}; Lecoanet, D.; and Cantiello, M. 
        \href{https://iopscience.iop.org/article/10.3847/1538-4357/ac5f08}{ApJ 929, 182.}
	  }
	  {Convective Penetration in Early-Type Stars}

\cvpub{}
	  {9}
	  {
		\textbf{Anders, E.H.}; Jermyn, A.S.; Lecoanet, D.; Fraser, A.E.; Cresswell, I.G.; Joyce, M.; and Fuentes, J.R. 
        \href{https://iopscience.iop.org/article/10.3847/2041-8213/ac5cb5}{ApJL 928, L10}.
	  }
	  {Schwarzschild and Ledoux are equivalent on evolutionary timescales}

\cvpub{}
	  {8}
	  {
		Jermyn, A.S.; \textbf{Anders, E.H.}; and Cantiello, M. 
        \href{https://iopscience.iop.org/article/10.3847/1538-4357/ac4e89}{ApJ 926, 221}.
	  }
	  {A Transparent Window into Early-Type Stellar Variability}

\cvpub{}
	  {7}
	  {
		\textbf{Anders, E.H.}; Jermyn, A.S.; Lecoanet, D.; and Brown, B.P., 
        \href{https://iopscience.iop.org/article/10.3847/1538-4357/ac408d}{ApJ 926, 169}.
	  }
	  {Stellar convective penetration: parameterized theory and dynamical simulations}

\cvpub{}
	  {6}
	  {
		Lecoanet, D.; Cantiello, M.; \textbf{Anders, E.H.}; Quataert, E.; Couston, L.; Bouffard, M.; Favier, B.; and Le Bars, M.,
          \href{https://doi.org/10.1093/mnras/stab2524}{MNRAS 508, 1, 132-143.}
	  }
	  {Surface Manifestation of Stochastically Excited Internal Gravity Waves}

\cvpub{2020}
	  {5}
	  {
		  \textbf{Anders, E.H.}; Vasil, G.M.; Brown, B.P.; and Korre, Lydia, 
		  \href{https://journals.aps.org/prfluids/abstract/10.1103/PhysRevFluids.5.083501}{Physical Review Fluids 5, 083501.}
	  }
	  {Convective dynamics with mixed temperature boundary conditions: why thermal relaxation matters and how to accelerate it}

\cvpub{2019}
	  {4}
	  {
		  \textbf{Anders, E.H.}; Lecoanet, D.; and Brown, B.P., 
		  \href{https://iopscience.iop.org/article/10.3847/1538-4357/ab3644}{ApJ 884, 65.}
	  }
	  {Entropy Rain: Dilution and Compression of Thermals in Stratified Domains}

\cvpub{}
	  {3}
	  {
		  \textbf{Anders, E.H.}; Manduca, C.M.; Brown, B.P.; Oishi, J.S.; Vasil, G.M., 
		  \href{https://iopscience.iop.org/article/10.3847/1538-4357/aaff61}{ApJ 872, 2.}
	  }
	  {Predicting the Rossby Number in Convective Experiments}

\cvpub{2018}
	  {2}
	  {
		  \textbf{Anders, E.H.}; Brown, B.P; and Oishi, J. S.,
		  \href{https://journals.aps.org/prfluids/abstract/10.1103/PhysRevFluids.3.083502}{Physical Review Fluids 3, 083502.}
	  }
	  {Accelerated evolution of convective simulations}

\cvpub{2017}
	  {1}
	  {
		  \textbf{Anders, E.H.} and Brown, B.P.,
		  \href{https://journals.aps.org/prfluids/abstract/10.1103/PhysRevFluids.2.083501}{Physical Review Fluids 2, 083501.}
	  }
	  {Convective heat transport in stratified atmospheres at low and high Mach number}
