\documentclass[11pt, preprint]{aastex}

%%%%%%begin preamble
\usepackage[hmargin=1in, vmargin=1in]{geometry} % Margins
\usepackage{hyperref}
\usepackage{url}
\usepackage{times}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{import}
\usepackage{pdfpages} % breaks with aastex6
%\usepackage{fontspec}
%\setmainfont{TimesNewRoman}
%\definetypeface[Serapion][rm][Xserif][Serapion Pro]
%\setupbodyfont[Serapion, 12pt]

%%%
%%%%%% uncomment following 4 lines to adjust title size/shape and
%%%%%% trailing space
%% \usepackage{titling}
%% %\pretitle{\noindent\Large\bfseries}
%% \date{}
%% \setlength{\droptitle}{-1in}
%\posttitle{\\}

\hypersetup{
     colorlinks   = true,
     citecolor    = gray,
     urlcolor      = gray
}

%% headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{}
\cfoot{\thepage}
\rfoot{}

\newcommand{\nosection}[1]{%
  \refstepcounter{section}%
  \addcontentsline{toc}{section}{\protect\numberline{\thesection}#1}%
  \markright{#1}}
\newcommand{\nosubsection}[1]{%
  \refstepcounter{subsection}%
  \addcontentsline{toc}{subsection}{\protect\numberline{\thesubsection}#1}%
  \markright{#1}}

\usepackage{titlesec}
%\titleformat{\abstract}[runin]{\normalfont\normalsize\bfseries}{\theabstract}{1em}{}
\titleformat{\section}[block]{\normalfont\fontsize{14pt}{17pt}\selectfont\bfseries\filcenter}{\thesection}{1em}{}
\titleformat{\subsection}[block]{\normalfont\normalsize\bfseries\filcenter}{\thesubsection}{1em}{}
\titleformat{\subsubsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsubsection}{1em}{}




%%%%%%end preamble

\begin{document}
\begin{center}
\huge{Evan H. Anders}\\
\large{Biographical Sketch}\\
\small{Department of Astrophysical and Planetary Sciences\\
University of Colorado, Boulder \\\texttt{evan.anders@colorado.edu}}
\end{center}


\vspace{-1.4cm}
\section*{Professional Preparation}
\vspace{-0.5cm}
\begin{tabular}{lll}
  Whitworth University & Physics & BS May 2014\\
  University of Colorado, Boulder & Astrophysics & MS December 2017\\
  University of Colorado, Boulder & Astrophysics & PhD Expected May 2020\\
\end{tabular}

\vspace{-1cm}
\section*{Appointments}
\vspace{-0.5cm}
\begin{tabular}{lll}
  NASA NESSF/FINESST Fellow & University of Colorado, Boulder & Sept 2018 -- \\
  George Ellery Hale Fellow & University of Colorado, Boulder & Sept 2015 -- Aug 2018 \\
\end{tabular}

\vspace{-1cm}
\section*{Publications}
\vspace{-0.5cm}

\subsection*{Publications most closely related to the proposed project}
\vspace{-13pt}
\begin{itemize}
\setlength{\itemsep}{-\parsep}
\setlength{\topsep}{-2\parsep}
\setlength{\partopsep}{-2\parsep}

\item \textbf{Anders}, E.~H., Lecoanet, D., \& Brown, B.~P.,
``Entropy Rain: Dilution and Compression of Thermals in Stratified Domains,''
2019, \href{https://iopscience.iop.org/article/10.3847/1538-4357/ab3644}{\emph{The Astrophysical Journal} 884,~1:65.}

\item \textbf{Anders}, E.~H., Manduca, C.~M., Brown, B.~P., Oishi, J.~S., \& Vasil, G.~M.,
``Predicting the Rossby Number in Convective experiments,''
2019, \href{https://iopscience.iop.org/article/10.3847/1538-4357/aaff61}{\emph{The Astrophysical Journal} 872,~2:138.}

\item \textbf{Anders}, E.~H., Brown, B.~P., \& Oishi, J.~S.,
``Accelerated evolution of convective simulations,''
2018, \href{https://journals.aps.org/prfluids/abstract/10.1103/PhysRevFluids.3.083502}{\emph{Physical Review Fluids} 3,~8:083502.}

\item \textbf{Anders}, E.~H. \& Brown, B.~P.,
``Convective heat transport in stratified atmospheres at low and high Mach number,''
2018, \href{https://journals.aps.org/prfluids/abstract/10.1103/PhysRevFluids.2.083501}{\emph{Physical Review Fluids} 2,~8:083501.}
\end{itemize}

\vspace{-38pt}
\subsection*{Other Publications}
\vspace{-13pt}
\begin{itemize}
\setlength{\itemsep}{-\parsep}
\setlength{\topsep}{-2\parsep}
\setlength{\partopsep}{-2\parsep}
\item Karki, S., Tuyenbayev, D., Kandhasamy, S., Abbott, B.~P., Abbott, T.~D., \textbf{Anders}, E.~H., Berliner, J., Betzwieser, J., Cahillane, C., Canete, L., Conley, C., Daveloza, H.~P., De Lillo, N., Gleason, J.~R., Goetz, E., Izumi, K., Kissel, J.~S., Mendell, G., Quetschke, V., Rodruck, M., Sachdev, S., Sadecki, T., Schwinberg, P.~B., Sottile, A., Wade, M., Weinstein, A.~J., West, M., and Savage, R.~L.,
``The Advanced LIGO photon calibrators,''
2016, \href{https://aip.scitation.org/doi/10.1063/1.4967303}{\emph{Review of Scientific Instruments} 87,~11:114503}
\end{itemize}

\vspace{-1.4cm}
\section*{Synergistic activities}
\vspace{-0.5cm}
\begin{itemize}
\setlength{\itemsep}{-\parsep}
\setlength{\topsep}{-2\parsep}
\setlength{\partopsep}{-2\parsep}
\item I participated in UC Santa Cruz's ISEE Professional Development Program twice, where I created and taught pedagogically-sound outreach modules to teach entering college freshmen about exoplanet transits (year 1) and buoyancy (year 2).  
\item I served on many committees at CU Boulder, including multiple years on the graduate admissions committee, where I led the development and use of rubrics in the graduate admissions process to ensure more equitable evaluation of applicants.
\setlength{\itemsep}{-\parsep}
\setlength{\topsep}{-2\parsep}
\setlength{\partopsep}{-2\parsep}
\item I served as an administrator of the CU Boulder Science, Technology, and Astronomy RecruitS (CU-STARS) program for three years, with duties including coordinating outreach trips to high schools, mentoring undergraduates, and designing hands-on activities in exoplanetary science, black holes, and atmospheric dynamics.
\item I helped mentor two undergraduate students in year-long projects; one of these projects eventually resulted in a publication (Anders, Manduca et al. 2019). 

\end{itemize}

\section*{Eligibility}
\vspace{-0.15cm}
\begin{itemize}
\setlength{\itemsep}{-\parsep}
\setlength{\topsep}{-2\parsep}
\setlength{\partopsep}{-2\parsep}
\item I, Evan H. Anders, am a citizen of the United States of America.
\item I will complete my doctoral degree in astrophysics before 1 October 2020.
\end{itemize}



\end{document}
