%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Conference Talks \& Posters}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Compressible Convection Conference $\cdot$ Sept. 2019} %conf title
    {International Conferences} % Category
    {} % Location
    {Newcastle, UK} % Date(s)
    {25-minute talk. ``Entropy Rain: Dilution and Compression of Turbulent Thermals in Stratified Domains''}

  \cventry
    {Stellar Hydro Days V $\cdot$ June 2019} 
    {} 
    {} 
    {Exeter, UK} % Date(s)
    {Speed talk \& Poster. ``Accelerating the evolution of atmospheric structure in convective simulations''} % Event

  \cventry
    {Compressible Convection Converence $\cdot$ Sept. 2017}
    {}
    {}
    {Lyon, France}
    {25-minute talk. ``Convective heat transport in stratified atmospheres at low and high Mach number''}

%---------------------------------------------------------
\end{cventries}


\begin{cventries}

%---------------------------------------------------------
  \cventry
    {APS Division of Fluid Dynamics $\cdot$ Nov. 2019} %conf title
    {Domestic Conferences} % Category
    {} % Location
    {Seattle, WA} % Date(s)
    {10-minute talk. ``Dilution and Compression of Thermals in Stratified Domains"}

  \cventry
    {American Astronomical Society 233 $\cdot$ Jan. 2019} 
    {} 
    {} 
    {Seattle, WA} % Date(s)
    {Poster. ``Accelerating the evolution of simulated convective atmospheres''} % Event

  \cventry
    {APS Division of Fluid Dynamics $\cdot$ Nov. 2018}
    {}
    {}
    {Atlanta, GA}
    {10-minute talk. ``Predicting the Rossby number in stratified, compressible convection''}

  \cventry
    {APS Division of Fluid Dynamics $\cdot$ Nov. 2017}
    {}
    {}
    {Denver, CO}
    {10-minute talk. ``The effects of Mach number and rotation on heat transport in stratified convection''}

  \cventry
    {APS Division of Fluid Dynamics $\cdot$ Nov. 2016}
    {}
    {}
    {Portland, OR}
    {10-minute talk. ``Sustained shear flows in stratified convection''}

  \cventry
    {AAS Solar Physics Division $\cdot$ June 2016}
    {}
    {}
    {Boulder, CO}
    {Poster. ``Boundary Layer Structure in Stratified Convection''}





%---------------------------------------------------------
\end{cventries}

