%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graduate Research Fellow / Assistant} % Job Title
    {CU Boulder \& LASP (Laboratory for Atmospheric and Space Physics)} % Organization
    {Boulder, CO} % Location
    {May 2015 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	  	\item { Published four first-author peer-reviewed journal articles. }
        \item { Gained proficiency creating, running, and analyzing massively parallel simulations using the \href{http://dedalus-project.org}{Dedalus} pseudospectral framework. }
		\item { Studied stratified, compressible convection and learned that it transports heats similarly to Boussinesq convection regardless of Mach number.}
		\item { Found a parameter, the ``Predictive Rossby Number,'' which controls the importance of rotational constraint on flows in convective simulations.}
		\item { Found and verified a mechanism for fast-forwarding past the long thermal relaxation of convective simulations, saving up to an order of magnitude of CPU time.} 
		\item { Derived a laminar theory for the propagation of buoyant vortex rings in stratified atmospheres, a potentially important heat transport mechanism in stellar envelopes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {NSF SURF Fellow} % Job title
    {LIGO (Laser Interferometer Gravitational-Wave Observatory)} % Organization
    {Hanford, WA} % Location
    {Summer 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a generalized Python script for analyzing calibration lines in LIGO's power spectrum.}
        \item {Determined error in LIGO's measurements using known input forcings from LIGO's photon calibration system.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DOE SULI Intern} % Job title
    {PNNL (Pacific Northwest National Laboratory)} % Organizatio)n
    {Richland, WA} % Location
    {Summer 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Optimized functions in GAiN (Global Arrays in NumPy), a Python module which applies PNNL’s Global Arrays parallel
        programming toolkit to the NumPy Python module.}
        \item {Designed new parallel algorithms for the GAiN `reduce' function and developed the foundation of the GAiN `master-slave' interface.}
      \end{cvitems} 
    }


%---------------------------------------------------------
\end{cventries}
